Cluster Difference Imaging Photometric Survey. II. TOI~837: A Young Validated Planet in IC~2602

### 2020-08-06 paper/ms.tex
add abstract for AAS
update manuscript

To advance the young planet census, we have been using data from the
TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, we had made $\sim$$6\times10^5$ light curves from
the first year of TESS observations. The light curves are available at
MAST\footnote{\stscilink}, and through \datasetlink.  Searching
through a subset of these light curves brought our attention to the
candidate transiting planet, \pn, that is the subject of this
analysis.

@@

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
the tenth and eleventh sectors of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were co-added and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also co-added into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1-13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, the ghost diagnostic
test, and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips are
suggestive of a grazing transiting planet, recurring roughly every 8
days with a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models shown in these plots is described in
Section~\ref{subsec:planet}.

@@

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
\texttt{2020-07-08}. } value is available.  We suspect that the
photometric failure to produce an $Rp$ magnitude as well as its poor
astrometric fit are due to blending with \tn.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescop at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT) with a cadence of $50\,$s (exposure time
of $25\,$s, readout and processing overhead of $25\,$s).  Except for
12 May, our observations were conducted under stable weather
conditions, with clear skies, temperatures of about $-70^\circ$C, and
wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
exclude from the analysis all data collected on May 12. We found that
the optimal calibrated light curves of \tn\ correspond to an 11 pixel
(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
observations carried out on June and May, respectively.  The data are
reported in Table~\ref{tab:phot}, and plotted in
Figure~\ref{fig:groundphot}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

Reconnaissance spectroscopic follow-up is an essential step in vetting
planet candidates.  Medium to high-resolution spectra enable physical
characterization of the star and therefore planet.  Reducing multiple
spectra to a radial velocity time-series can enable planet mass
measurements, and also set limits on the mass of any nearby
companions.  Finally, if there are close or bright companions,
reconnaissance spectra can also reveal the presence of a secondary set
of stellar lines.

@@

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
In this Section we describe each constraint in turn, and then present
a calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
demonstrate that the probability \tn\ is an astrophysical false
positive is small enough to validate it as a planet.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host blend together, and reduce the ``true'' TESS-band eclipse
depth $\delta_{\rm true}$ to the observed depth $\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
\end{equation}
where the total system flux and the flux from only the companion
(``comp'') binary are labeled appropriately.  The requirement that the
eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
system:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10}
             \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

@@

\paragraph{Multicolor photometry and HEB scenarios}
The most plausible HEB scenarios for \tn\ involve pairs of eclipsing M
dwarfs (Figure~\ref{fig:fpscenario}).  Eclipses of such stars are much
redder than eclipses of the G-dwarf \tn.  Limits on whether the
transit depth decreases in bluer bandpasses can therefore rule out
some HEB scenarios.

@@

For a fixed secondary mass, we then asked whether any tertiary
companions existed for which the maximal expected eclipse depth could
have been larger than the observed depth.  In cases for which the
answer was yes, we could not rule out such hierarchical eclipsing
binary systems.  Conversely, we ruled out systems for which at fixed
secondary mass no tertiary mass could enable eclipses of the necessary
depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The ${\rm
R_C}$-band limit corresponded to a secondary mass limit of $M_2 > 0.27
M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger limit of
$M_2 > 0.70 M_\odot$.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  with right ascension, declination, and parallax similar to \cn.
  They are selected by drawing from a $(\alpha, \delta, \pi)$ cube
  centered on the cluster with boundaries set at $5\times$ the
  standard deviation in the cluster parameters.  $G$ denotes Gaia
  broadband magnitudes, $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST
  isochrones (colored lines) fit the upper main sequence well, but
  diverge from the data for $M_\star \lesssim 0.7 M_\odot$. This is a
  known issue with the M dwarf models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Youth diagnostics.}
  {\it Top:} Rotation periods for \tn\ and selected open clusters.
  The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
  (1000$\,$Myr) are shown.  Their rotation periods were measured by
  \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
  open clusters.  The field star sample is drawn from Kepler planet
  hosts, and was measured by \citet{berger_identifying_2018} using
  Keck-HIRES.  The young open clusters members were surveyed by
  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
  lithium depletion boundary ages for these clusters of
  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
    \label{fig:lithium_rotation}
	}
\end{figure}

@@

We opted for this approach rather than a joint fit of the photometry
and radial velocities because the RVs on their own did not show
evidence for a planetary signal.  Our preference for using only the
TESS data to derive the transit parameters was in our view justified
by the systematic uncertainties inherent to ground-based light curve
production, particularly in comparison star selection.  Our assumption
of a constant radius across all bandpasses was tested by independently
fitting each ground-based transit while letting the planetary radius
float (Section~\ref{subsec:colorphot}). The transit depths did not
significantly change between different bandpasses.
Our assumption in the false-positive probability calculation
(Section~\ref{subsec:fpp}) of no odd-even variations was tested by
independently fitting all odd and all even transits separately.
The resulting best-fit depths were consistent within 1-$\sigma$.
% odd: (Rp/R*)^2 = 0.005500 +0.000558 -0.000169
% even: (Rp/R*)^2 = 0.005659 +0.000636 -0.000185

@@

The easiest way to definitively confirm the planetary nature of \tn\
will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
signal consistent with the photometric transit would rule out BEB and
HEB scenarios, as it would imply that the eclipsing object is bound to
the target star. Combined with our non-detection of the planet's mass
from radial velocity monitoring, this would confirm that \pn\ is a
planet.

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - c_1 ( 1 - \mu ) - c_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
  \label{eq:ephem}
\end{align}
% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's contraction and photoevaporation.  If an
RV campaign were timed to coincide with TESS sectors 36 and 37 (3
March 2021 through 28 April 2021), it would significantly ease
extraction of the Keplerian signal.  The reason is that the RVs,
activity indicators, and photometry could be modeled simultaneously
\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
Combining photometric and radial velocity data from non-overlapping
epochs would also constrain the models, but perhaps not quite as
convincingly.

>>>>

To advance the young planet census, we have been using data from the
TESS spacecraft \citep{ricker_transiting_2015} to perform a Cluster
Difference Imaging Photometric Survey
\citep[CDIPS;][]{bouma_cluster_2019}.  Our targets in this survey are
candidate young stars that have been reported in the literature.  At
the time of writing, $\sim$$6\times10^5$ light curves from
Year 1 of TESS had been created and were available through
MAST\footnote{\stscilink}, and via \datasetlink.  Searching
through a subset of these light curves brought our attention to the
candidate transiting planet, \pn, that is the subject of this
analysis.

@@

\tn\ was observed by TESS from 26 March 2019 until 20 May 2019, during
Sector 10 and Sector 11 of science operations
\citep{ricker_transiting_2015}.  The star was designated
TIC\,460205581 in the TESS Input Catalog
\citep{stassun_TIC_2018,stassun_TIC8_2019}.  Pixel data for an
$11\times11$ array surrounding the star were co-added and saved at
2-minute cadence.  The $2048\times2048$ image from the entire CCD was
also co-added into 30-minute stacks, and saved as a ``full frame
image'' (FFI).

The TESS Science Processing Operations Center
\citep{jenkins_tess_2016} processed the image data and identified the
transiting planet signature from two transits in
Sector 10, again with three transits in Sector 11, and then for a
final time when Sectors 1--13 were searched at the end of the first
year of the mission. The transit signature was fitted with a
limb-darkened transit model \citep{li_kepler_2019} and passed all the
diagnostic tests \citep{twicken_kepler_2018}, including the odd/even
depth test, the weak secondary eclipse test, the ghost diagnostic
test, and the difference image centroiding test, which placed the
transit source within $\sim$2 arcsec of the location of TOI~837. No
additional transit-like features were identified in any of the SPOC
searches. The TESS Science Office alerted the community to this
candidate transiting planet on 17 June 2019.  Our subsequent blind
search of the CDIPS FFI light curves also showed the transits. Given
that the 2-minute data had better sampling cadence, we opted to use
the Presearch Data Conditioning (PDC) light curve with the default
aperture for our
analysis~\citep{smith_kepler_2012,stumpe_multiscale_2014,smith_finding_2016}.

Figure~\ref{fig:tessphot} shows the data.  The dominant modulation
induced by starspots coming into and out of view has a peak-to-peak
amplitude of about 2.3\%, and a period of about 3 days.  The dips are
suggestive of a grazing transiting planet, recurring roughly every 8
days with a depth of about 0.4\%.  A few flares are also visible.  A
phase-folded view of the TESS transits with starspot variability
removed is also shown in Figure~\ref{fig:tessphot}. Our fitting procedure
for the models in these plots is described in
Section~\ref{subsec:planet}.

@@

The Gaia DR2 data for Star A seems poorly behaved.  While Star A has
$G=15.1$, and $Bp=14.9$, no $Rp$ magnitude is reported.
Correspondingly, no RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412},
\texttt{2020-07-08}. } value is available.  We suspect that the
photometric failure to produce an $Rp$ magnitude as well as the poor
astrometric fit of this star are due to blending with \tn.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.48\textwidth]{f3.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Ground-based follow-up photometry.} The data were acquired
    using the 0.36$\,$m telescope at El Sauce and the 0.40$\,$m
    ASTEP400 telescope at Dome C.  Black points represent the
    measurements after binning at 10-minute intervals. The gray line
    is the model that best fits the combined TESS and ground-based
    data.  Red and blue lines show 2-$\sigma$ lower limits on the
    transit depths in the Cousins-R and Johnson-B bandpasses used to
    rule out specific false positive scenarios (see
    Section~\ref{subsec:colorphot}).
		\label{fig:groundphot}
	}
\end{figure}

@@

\tn\ was observed with ASTEP on 12 May 2020, 29 May 2020, 14 June
2020, and 23 June 2020 (UT).  Except for
12 May, our observations were conducted under stable weather
conditions, with clear skies, temperatures of about $-70^\circ$C, and
wind speeds less than 5\,m$\,$s$^{-1}$. Due to their poor quality, we
exclude from the analysis all data collected on 12 May. We found that
the optimal calibrated light curves of \tn\ correspond to an 11 pixel
(10\,arcsec) and 14 pixel (12\,arcsec) radius aperture for
observations carried out on June and May, respectively.  The data are
reported in Table~\ref{tab:phot}, and plotted in
Figure~\ref{fig:groundphot}.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=.47\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Velocimetry of \tn.} {\it Top:} Radial velocity (RV)
    measurements, with best-fit instrument offsets and jitter terms
    included.  The expected scatter from starspots based on $v\sin i$
    and the photometric modulation amplitude is
    $\sim$300$\,$m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The dashed black
    line shows a circular Keplerian orbit representing the 3-$\sigma$
    upper mass limit.
    \label{fig:rvs}
	}
\end{figure}

Reconnaissance spectroscopic follow-up is an essential step in vetting
planet candidates.  Medium to high-resolution spectra enable physical
characterization of the star and therefore planet.  Reducing multiple
spectra to radial velocities can enable planet mass
measurements, and can also lead to limits on the mass of nearby
companions.  Finally, if there are close or bright companions,
reconnaissance spectra can also reveal the presence of a secondary set
of stellar lines.

@@

Figure~\ref{fig:fpscenario} provides a visual summary of the possible
astrophysical false positive scenarios, as well as our ability to rule
them out based on our combined photometry, velocimetry, and imaging.
In this Section we describe each constraint in turn, and then present
a calculation using \texttt{VESPA} \citep{morton_efficient_2012} to
demonstrate that the probability of \tn\ being an astrophysical false
positive is small enough to validate it as a planet.

@@

\subsubsection{Transit Depth}
In HEB and BEB scenarios, the flux from \tn\ and the true eclipsing
binary host blend together, and reduce the ``true'' TESS-band eclipse
depth $\delta_{\rm true}$ to the observed depth $\delta_{\rm obs}$:
\begin{equation}
  \delta_{\rm obs}
  = 
  \delta_{\rm true} \frac{F_{\rm comp}}{F_{\rm total}},
\end{equation}
where the total system flux and the flux from only the companion
(``comp'') binary are labeled as such.  The requirement that the
eclipse is produced by fusion-powered stars and that $\delta_{\rm true} < 0.5$
translates to a bound on the faintest possible blended companion
system:
\begin{equation}
  \Delta m < -\frac{5}{2} \log_{10}
             \left( \frac{0.5}{\delta_{\rm obs}} \right).
\end{equation}
For \tn\ ($T=9.93$), this implies that any stellar companion invoked
to explain the transit depth must be brighter than $T=15.07$.  In
Figure~\ref{fig:fpscenario}, we set the spatial limit to 2$''$ based
on the precision at which we have localized the transits using
seeing-limited ground-based photometry.

@@

\paragraph{Multicolor photometry and HEB scenarios}
The most plausible HEB scenarios for \tn\ involve pairs of eclipsing M
dwarfs (Figure~\ref{fig:fpscenario}).  Eclipses of such stars are much
redder than eclipses of the G-dwarf \tn.  Limits on whether the
transit depth decreases in bluer bandpasses can therefore rule out
certain HEB scenarios.

@@

For a fixed secondary mass, we then asked whether any tertiary
companions existed for which the maximal expected eclipse depth could
have been larger than the observed depth.  
We could not rule out hierarchical eclipsing binary systems in cases
for which the answer was yes.
Conversely, we ruled out systems for which at fixed
secondary mass no tertiary mass could enable eclipses of the necessary
depth (in ${\rm R_C}$-band, or in ${\rm B_J}$-band).  The ${\rm
R_C}$-band limit corresponded to a secondary mass limit of $M_2 > 0.27
M_\odot$, and the ${\rm B_J}$-band corresponded to a stronger limit of
$M_2 > 0.70 M_\odot$.

@@

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{ 
  {\bf Hertzsprung-Russell diagram of \tn\ and members of \cn.}
  Members (black circles) were identified by
  \citet{cantatgaudin_gaia_2018}.  Gray circles are non-member stars
  with right ascension, declination, and parallax similar to \cn.
  They are selected by drawing from a $\{\alpha, \delta, \pi\}$ cube
  centered on the cluster with boundaries set at $5\times$ the
  standard deviation in the cluster parameters.  $G$ denotes Gaia
  broadband magnitudes, $Bp$ Gaia blue, and $Rp$ Gaia red.  MIST
  isochrones (colored lines) fit the upper main sequence well, but
  diverge from the data for $M_\star \lesssim 0.7 M_\odot$. This is a
  known issue with the M dwarf models (see Section~\ref{subsec:hr}).
  \label{fig:hr}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.45\textwidth]{f9b.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{ {\bf Youth diagnostics.}
  {\it Top:} Rotation periods for \tn\ and selected open clusters.
  The Pleiades (120$\,$Myr), Praesepe (670$\,$Myr), and NGC$\,$6811
  (1000$\,$Myr) are shown.  Their rotation periods were measured by
  \citet{rebull_rotation_2016a,douglas_poking_2017,douglas_k2_2019},
  and \citet{curtis_temporary_2019}, respectively.  {\it Bottom:}
  Lithium 6708\AA\ equivalent widths for \tn, field stars, and young
  open clusters.  The field star sample is drawn from Kepler planet
  hosts, and was measured by \citet{berger_identifying_2018} using
  Keck-HIRES.  The young open cluster members were surveyed by
  \citet{randich_gaiaeso_2018} using the UVES and GIRAFFE
  spectrographs at the ESO VLT.  \citet{randich_gaiaeso_2018} found
  lithium depletion boundary ages for these clusters of
  $37.7^{+5.7}_{-4.8}\,{\rm Myr}$ (NGC$\,$2547) and
  $43.7^{+4.3}_{-3.9}\,{\rm Myr}$ (\cn).  
    \label{fig:lithium_rotation}
	}
\end{figure}

@@

We opted for this approach rather than a joint fit of the photometry
and radial velocities because the RVs on their own did not show
evidence for a planetary signal.  Our preference for using only the
TESS data to derive the transit parameters was in our view justified
by the systematic uncertainties inherent to ground-based light curve
production, particularly in comparison star selection.  Our assumption
of a constant radius across all bandpasses was tested by independently
fitting each ground-based transit while letting the planetary radius
float (Section~\ref{subsec:colorphot}). The transit depths did not
significantly change between different bandpasses.
Our assumption in the false-positive probability calculation
(Section~\ref{subsec:fpp}) of no odd-even variations was tested by
independently fitting all odd and all even transits separately.
The resulting best-fit depths were consistent within 1-$\sigma$.
% odd:  log(r/rs) = -2.601528 +0.048317 -0.015647
% even: log(r/rs) = -2.587273 +0.053236 -0.016607

@@

The easiest way to confirm the planetary nature of \tn\
will be a Rossiter-McLaughlin (RM) measurement.  Detection of an RM
signal consistent with the photometric transit would rule out BEB and
HEB scenarios, as it would imply that the eclipsing object is bound to
the target star. Combined with our non-detection of the planet's mass
from radial velocity monitoring, this would confirm that \pn\ is a
planet.

The maximum amplitude of the Rossiter-McLaughlin anomaly is
\citep{gaudi_prospects_2007}
\begin{align}
  \Delta V_{\rm RM} &\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
  \approx 14\,{\rm m\,s}^{-1},
\end{align}
for
\begin{align}
  f_{\rm LD} &= 1 - u_1 ( 1 - \mu ) - u_2 (1 - \mu )^2,
\end{align}
where $\mu \approx (1 - b^2)^{1/2}$, $u_i$ are the limb-darkening
parameters, and for calculation purposes we
assumed $b=0.95$ and used stellar and transit parameters from
Tables~\ref{tab:starparams} and~\ref{tab:posterior}.  Although
challenging, for a 1.9$\,$hr transit of a $V=10.6$ star, a detection
could be achieved with modern spectrographs.  The next viable total
transit windows from Chile occur in January and February of 2021;
there are also a few visible per season from other southern locations.
The most precise available ephemeris, found from our joint fit of the
TESS and ground-based photometry, is as follows.
\begin{align}
  t_0\ [{\rm BJD_{TDB}}] &= 2458574.272523 \pm 0.000594 \nonumber \\
  P\ [{\rm d}] &= 8.3248762 \pm 0.0000156 \nonumber \\
  T_{14}\ [{\rm hr}] &= 1.86 \pm 0.04.
  \label{eq:ephem}
\end{align}
% /Users/luke/Dropbox/proj/timmy/results/TOI_837_allindivtransit_phot_results/20200711/posterior_table_clean_allindivtransit.tex

@@

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's contraction and photoevaporation.  If an
RV campaign were timed to coincide with TESS Sectors 36 and 37 (3
March 2021 through 28 April 2021), it would significantly ease
extraction of the Keplerian signal.  The reason is that the RVs,
activity indicators, and photometry could be modeled simultaneously
\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
Combining photometric and radial velocity data from non-overlapping
epochs would also constrain the models, but perhaps not quite as
convincingly.
